---
title: "ggplot_intro"
output: html_document
---

plan...here we right in markdown
##harshtags means headers

```{r}
here we write in rcode


You can also embed plots, for example:
# load libraries
```{r, echo=FALSE}
library(dplyr)
library(gapminder)
library(ggplot2)
install.packages('ggplot2')
G <-gapminder%>%
  filter(year ==2007)%>%
  mutate(pop_m = pop/1e6)
```
#my first plot
```{r}
S <-ggplot(G, aes(x = gdpPercap, y = lifeExp)) + geom_point()
S
```
#My second plot
```{r}
S2 =S + aes(size = pop_m)
S2
S3 = S2 + aes(color= continent)
S3
S <- ggplot (g, aes(x = gdpPercap, y = lifeExp))+
  geom_point()+
  aes(size = pop_m)+
  aes(color = continent)+
  ggtitle('Health and Health of nations for 2007') +
  xlab('GDP perCapita (USD/year'))+
  ylab('life Expectancy(years'))+
  scale_color_discrete('Continent')+
  scale_size_continuous('Population (M)')
S


```
#My boxplot
```{r}
b <-ggplot(G, aes(x = continent, y = lifeExp))+
  geom_boxplot()+
  aes(fill=continent)+
  theme(legend.position='none')
b
```


```

